---
title: "Statistical Inference Project (Simulation)"
author: "Andrea Bisognin"
date: "18/10/2014"
output: pdf_document
---

```{r generate-data}
suppressPackageStartupMessages(library(ggplot2))
set.seed(42)
n <- 40 
lambda <- 0.2
nsim <- 1000
simulations <- sapply(seq_len(nsim),function(x){
        data <- rexp(n,lambda)
        mean(data)
})

sims <- data.frame(x=simulations)
```

## Show where the distribution is centered and compare it to the theoretical centre center of the distribution 

```{r}
theor_mean = 1/lambda
actual_mean= mean(simulations)
```


Theoretical mean of the distribution  $\mu = \frac{1}{\lambda}$ is `r theor_mean` while actual simulated mean is `r actual_mean`.

```{r density,fig.height=3,fig.width=7}
ggplot(aes(x=x),data=sims) + geom_density() +
        geom_vline(xintercept=theor_mean,color="red") + 
        geom_vline(xintercept=actual_mean,color="black") +
        stat_function(fun=dnorm,args=list(mean=theor_mean,sd=sqrt(theor_variance)),color="green")
```



## Show how variable it is and compare it to the theoretical variance of the distribution.

```{r}
theor_variance = 1/(lambda^2*n)
actual_variance = var(simulations)
```


Theoretical variance of the distribution $Var(X) = \frac{1}{n \lambda^2}$ is `r theor_variance` while actual simulated variance is `r actual_variance`.

## Show that the distribution is approximately normal

## Evaluate the coverage of the confidence interval for $\frac{1}{\lambda}: \bar{X} \pm 1.96 \frac{s}{\sqrt{n}}$  

