---
title: "ToothGrowth"
author: "Andrea Bisognin"
date: "Thursday, October 23, 2014"
output: pdf_document
---

# Load and perform some basic exploratory data analyses

```{r load-data,fig.height=3,fig.width=4}
data(ToothGrowth)
library(lattice)
bwplot(len ~ I(factor(dose)) | supp, data=ToothGrowth)
```

# Provide a basic summary of the data

```{r summary}
library(plyr)
ddply(ToothGrowth,.(supp,dose), summarize, mean=mean(len),sd=sd(len),n.obs=length(len))
```


# Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose.




```{r ci-tests}
the.tests <- lapply( unique(ToothGrowth$dose) ,function(x) t.test(len ~ supp ,ToothGrowth,subset=ToothGrowth$dose == x))
names(the.tests) <- unique(ToothGrowth$dose)
the.tests
```

# State your conclusions and the assumptions needed for your conclusions. 

## Assumptions

I'm assuming tooth length is approximately normal. Quantile-quantile plot is in agreement with this hypotheses.
To be cautious i don't assume common variance.

```{r assumptions,fig.width=4,fig.height=4}
qqnorm(  with( ToothGrowth, (len - mean(len))/sd(len) )  )
abline(a=0,b=1,lw=3,col="red")
```

## Conclusions

Orange juice is more effective (at alpha=.05) then ascorbic acid tablets at the 0.5 mg and 1.0 mg dose levels whereas at the 2.0 mg dose level there is no detectable difference 